Improving the prospects for multimessenger astronomy with \earlywarning\ detection of compact binary coalescence.

### 2011-05-05 introduction.tex
Put first paragraph back in
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@744 ccdd05d5-56c1-461a-bf98-85f6876523b4

%
\begin{comment}
The coalescence of compact binary systems consisting of neutron stars (NS)
and/or black holes (BH) is the most promising source of gravitational radiation
for Advanced \LIGO~\cite{ALIGOWeb}, Virgo~\cite{AVirgoWeb}, \GEO~\cite{GEOWeb}, and
\LCGT~\cite{LCGTWeb}.  Tens of
binary coalescence events are expected to be observed in the
advanced detector era later this decade~\cite{Abadie:2010p10836}.
\end{comment}

As a binary system loses energy to gravitational waves, its orbital separation
decreases. This causes a run-away inspiral with the gravitational-wave
amplitude and frequency increasing until the system eventually merges near the
innermost stable circular orbit (\ISCO).  If a neutron star is involved it may become tidally disrupted near the merger.
This disrupted matter can fuel a bright electromagnetic
counterpart in the system's final moments as a binary~\cite{shibata:2007}.
In order to observe the prompt and
potentially most intense electromagnetic emission, telescopes must point during the seconds surrounding the
merger.

>>>>

\editorial{Would the introduction be more effective without this paragraph?} The coalescence of compact binary systems consisting of neutron stars (NS)
and/or black holes (BH) is the most promising source of gravitational radiation
for Advanced \LIGO~\cite{ALIGOWeb}, Virgo~\cite{AVirgoWeb}, \GEO~\cite{GEOWeb}, and
\LCGT~\cite{LCGTWeb}.  Tens of
binary coalescence events are expected to be observed in the
advanced detector era later this decade~\cite{Abadie:2010p10836}.

As a compact binary system loses energy to gravitational waves, its orbital separation
decreases. This causes a run-away inspiral with the gravitational-wave
amplitude and frequency increasing until the system eventually merges near the
innermost stable circular orbit (\ISCO).  If a neutron star is involved it may become tidally disrupted near the merger.
This disrupted matter can fuel a bright electromagnetic
counterpart in the system's final moments as a binary~\cite{shibata:2007}.
In order to observe the prompt and
potentially most intense electromagnetic emission, telescopes must point during the seconds surrounding the
merger.
